
library(osmar) # loads osmar libarary which downloads data from openstreetmap as puts it into a dataframe
library(rgeos) # geometry library get area in metres squared
library(rgdal) # projection linrary to transform projection
 library(rCharts) # 
 library(rjson)
 require(plyr)
 library(RColorBrewer)
 library(httr)
 library(maptools)
 require(RGoogleDocs)
 library(devtools)
library(RCurl)
library(knitr) # create html webpage from this code
 library(sp)# library for spatial analysis - can plot 'graphs'/maps of sp objects
library(rgbif)
 library(SortableHTMLTables)



system("rm /home/tim/github/localtivate/Rscripts/orchards.geojson")
system("rm /home/tim/github/localtivate/Rscripts/orchards3.shp")
system("rm /home/tim/github/localtivate/Rscripts/orchards4.shp")
system("rm /home/tim/github/localtivate/Rscripts/orchards6.geojson")
system("wget -O /home/tim/github/localtivate/Rscripts/orchards.osm \"http://overpass-api.de/api/interpreter?data=way[%22leisure%22=%22common%22]%2855.30570111642547,-5.3887939453125,56.74669909639952,-2.49114990234375%29;out%20body;%3E;out%20skel;\"")
system("ogr2ogr -f GeoJSON /home/tim/github/localtivate/Rscripts/orchards.geojson /home/tim/R/Communitymapping/orchards.osm multipolygons")
json_orchards = '/home/tim/github/localtivate/Rscripts/orchards.geojson'

json_orchards <- fromJSON(paste(readLines(json_orchards), collapse=""))

system("ogr2ogr -f \"ESRI Shapefile\" /home/tim/github/localtivate/Rscripts/orchards3.shp /home/tim/github/localtivate/Rscripts/orchards.osm multipolygons")

x <- readShapeSpatial("/home/tim/github/localtivate/Rscripts/orchards3.shp")

o2 <- read.csv("duddingston_survey.csv")
o2$name <- o2$Unique.reference.number...your.initials.and.a.number.

merged <- merge(x=x@data, y=o2, by.x='localtivat', by.y='name', all.x=TRUE)
merged2 <- merged[,c("name","osm_way_id","leisure","Location.of.the.space","Which.of.the.following.categories.best.describes.the.space.","What.natural.features.are.present.","What.man.made.features.are.present.","Terrain","Exposure.and.Orientation","Current.uses","Does.this.space.have.an.official.name..How.do.local.people.usually.refer.to.it.","Accessibility","History.and.prior.uses.of.site","Comments.and.Extras","Unique.reference.number...your.initials.and.a.number.","Potential.future.uses")]
correct.ordering <- match(x@data$name, merged$name)
x@data <- merged[correct.ordering, ]
cbind(x@data$name, merged$name[correct.ordering])
writeSpatialShape(x, fn="/home/tim/github/localtivate/Rscripts/orchards4")
system("ogr2ogr -f GeoJSON /home/tim/github/localtivate/Rscripts/orchards6.geojson  /home/tim/R/Communitymapping/orchards4.shp")
json_orchards2 = '/home/tim/github/localtivate/Rscripts/orchards6.geojson'
json_orchards2 <- fromJSON(paste(readLines(json_orchards2), collapse=""))

json_orchards2$features <- lapply(json_orchards2$features, function(properties){within(properties, {
popup = iconv(whisker::whisker.render(
 '<b> Name: {{properties.name}} </b><br>
        <b>Other OpenStreetMap tags: </b> {{properties.other_tags}} <br>
  <b>Number of volunteers: </b> {{properties.number_of_}} <br>
  <b>Number of trees: </b> {{properties.number_of_2}} <br>
 <b>Active management: </b> {{properties.active_man}} <br>'    
), from = 'latin1', to = 'UTF-8')
})
})
```

```{r comment = NA, results = 'asis', tidy = F, message = F, echo=F}
outmap3 <- Leaflet$new()
outmap3$tileLayer(provider = 'Stamen.TonerLite')
outmap3$setView(c(55.830,-4.249), zoom = 13)
outmap3$geoJson(json_orchards2, 
  onEachFeature = '#! function(feature, layer){
    layer.bindPopup(feature.popup)
  } !#')
#out_map1$geoJson(geogovan)
outmap3$enablePopover(TRUE)
outmap3$print('char', include_assets=TRUE, cdn=TRUE)
```

<div class="custom-class" markdown="1" style="width:620px" align="justify"><p>Google spreadsheets can be private or public and equally the web map above could be used internally or externally depending
on requirements of the organisation.</p></div>

A demo Google spreadsheet has been created <a href="https://docs.google.com/spreadsheet/pub?key=0ArVD_Gwut6UBdEVwOVdXWDlQRXF1cm5vSF94MmN4ZGc&output=html" teargetr="_blank">here</a>

<div class="custom-class" markdown="1" style="width:620px" align="justify"><p>The demo spreadsheet currently uses fictional values for demonstration purposes which are linked to real orchard data live from OpenStreetMap. The two datasets are currently linked via 'name' category but other links based on location or reference codes could be used.</p>

<p>If data is updated on OpenStreetMap or on the Google document, this will be reflected on the map and table below. Currently the update
is daily, but could be run almost realtime if moved to a dedicated computer or server.</p></div>

Combined Table of values 
---------------------------------------------------

<div class="custom-class" markdown="1" style="width:620px" align="justify"><p>Table showing combined values from Google spreadsheet and openstreetmap</p></div>

```{r echo = F, message = F, cache = F, include=FALSE}
sortable.html.table(merged2, 'sample.html', '/home/tim/Dropbox/Public/Community mapping')
```

<iframe width="1200px" height="600px"" frameBorder='0' src="https://dl.dropboxusercontent.com/u/7033208/Community%20mapping/sample.html" allowfullscreen></iframe>


Technical details 
---------------------------------------------------

<div class="custom-class" markdown="1" style="width:620px" align="justify"><p>This map and table are created using a 'R' software script. It requires about 100 lines of code to download, merge and display the dataset. Using this R code may be difficult for those unfamiliar with it but I will publish this code and I am also happy to help people use it and setup a basic site free of charge (resource depending and for a good cause!).</p></div>


